Real-world Feasibility Analysis of ACT Algorithm for Robotic Manipulation on Home

### 2025-05-03 paper.tex
图片替换+居中
fix:新增表格调整居中
fix: 更改图片和表格标题

\begin{figure}
\includegraphics[width=\textwidth]{fig1.pdf}
\caption{(a) ACT implementation principles; (b) CVAE model architecture} \label{fig1}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{Left figure is leader arm,right figure is follower arm.} \label{fig2-1}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{Upper left figure is the initial state; upper right figure is the target state; bottom figure is the training environment} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{10}
\caption{Overall Workflow}
 \label{fig10}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=0.85\textwidth]{fig12.pdf}
\caption{Wrist-mounted camera position adjustment.} \label{fig12}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=323pt]{15}
\caption{  Loss curve for the first action} \label{fig14}
\end{figure}

@@

\begin{table}[H]
  \centering
    \caption{\small Validation Success Rates of Decomposed Actions}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{fig1.pdf}
\caption{ ACT implementation principles and  CVAE model architecture} \label{fig1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig3.pdf}
\caption{leader arm (Left) and follower arm(right).} \label{fig2-1}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.95\textwidth]{fig4.pdf}
  \caption{ initial state(upper left); target state(upper right);training environment(bottom)} \label{fig2}
  \end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{10}
\caption{Overall workflow}
 \label{fig10}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\textwidth]{fig12.pdf}
\caption{Wrist-mounted camera position adjustment.} \label{fig12}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=323pt]{fig15.pdf}
\caption{The loss curve for the first two actions during model training} \label{fig14}
\end{figure}

@@

\begin{table}[H]
  \centering
    \caption{\small Model training specifications}\label{tab2}
  \begin{tabularx}{\textwidth}{
      >{\centering\arraybackslash}p{0.8cm}     % 第一列固定宽度（窄）
      >{\centering\arraybackslash}X           % 第二列自动调整
      >{\centering\arraybackslash}X  
      >{\centering\arraybackslash}X           % 第四列自动调整
      >{\centering\arraybackslash}X           % 第五列自动调整
      >{\centering\arraybackslash}X           % 第六列自动调整
    }
\toprule
    \textbf{step} & \textbf{action} & \textbf{state} & \textbf{training time} & \textbf{episodes} & \textbf{success rate} \\
   \midrule
     1 & A --> B      & A[1234]-B[]-C[]       & 2h 7m 51s  & 90 & 9/10 \\
     2 & A --> C      & A[123]-B[4]-C[]       & 2h 14m 43s & 40 & 9/10 \\
     3 & B --> C      & A[12]-B[4]-C[3]       & 2h 11m 19s & 50 & 10/10 \\
     4 & A --> B      & A[12]-B[]-C[34]       & 3h 46m 55s & 40 & 10/10 \\
     5 & C --> A      & A[1]-B[2]-C[34]       & 2h 7m 44s  & 80 & 10/10 \\
     6 & C --> B      & A[14]-B[2]-C[3]       & 2h 24m 28s & 40 & 9/10 \\
     7 & A --> B      & A[14]-B[23]-C[]       & 4h 13m 50s & 40 & 9/10 \\
     8 & A --> C      & A[1]-B[234]-C[]       & 3h 13m 1s  & 40 & 10/10 \\
     9 & B --> C      & A[]-B[234]-C[1]       & 1h 59m 21s & 70 & 10/10 \\
     10 & B --> A     & A[]-B[23]-C[14]       & 1h 58m 55s & 60 & 10/10 \\
     11 & C --> A     & A[3]-B[2]-C[14]       & 2h 5m 1s   & 50 & 10/10 \\
     12 & B --> C     & A[34]-B[2]-C[1]       & 3h 2m 31s  & 40 & 9/10 \\
     13 & A --> B     & A[34]-B[]-C[12]       & 2h 0m 38s  & 60 & 10/10 \\
     14 & A --> C     & A[3]-B[4]-C[12]       & 3h 28m 24s & 40 & 9/10 \\
     15 & B --> C     & A[]-B[4]-C[123]       & 2h 11m 32s & 70 & 10/10 \\
     \bottomrule
  \end{tabularx}
\end{table}
